DNest4: An implementation of Diffusive Nested Sampling in C++11 and Python

### 2016-05-10 paper/ms.tex
Some sections

\title{DNest4: A C++11 implementation of Diffusive Nested Sampling}
\author{Brendon J. Brewer\\
Dan Foreman-Mackey}
\date{}

@@

\section{Introduction}

>>>>

\title{DNest4: An implementation of Diffusive Nested Sampling
in C++11 and Python}
\author{Brendon J. Brewer\\
Dan Foreman-Mackey}
\date{}

@@

\section{Bayesian computation, statistical mechanics, and Nested Sampling}

\subsection{Diffusive Nested Sampling}

\section{Basic usage of DNest4}

\section{Advanced usage}

\subsection{Multithreading}

\section{Implementing models}

\section{Python package}

% Assign to DFM

\section{Examples}

\subsection{}

\subsection{Approximate Bayesian Computation}
Nested Sampling can be used to solve ``Approximate Bayesian Computation''
problems elegantly and efficiently.
